Supplementary material for "Hack Weeks as a model for Data Science Education and Collaboration"

### 2018-06-21 why.tex
It all fits now!

There are several reasons to run a hack week of the sort described here.

\noindent\textbf{Education and Training}: While some hack weeks are focused more on education than others (see Figure \ref{fig:hackspectrum}), there is often a skill-development component in the form of tutorials and informal and peer learning. This type of lateral knowledge transfer \cite{b:wilson-swc-lessons-2016} is a core attribute of a hack week, and provides an opportunity to learn skills that are not described in papers and software implementations.

@@

\noindent\textbf{Community Building}: Hack weeks provide an opportunity to catalyze community development through a shared interest in solving computational challenges with open source software. These events allow computationally-minded researchers to break from the isolation of their academic departments and spark new collaborations.

\noindent\textbf{Interdisciplinary research}: Intensive, time-bounded collaborative events are an excellent opportunity to experiment with concepts, questions, and methods that span boundaries within and across disciplines. Despite the fact that interdisciplinary experiments are impactful \cite{Hall2012-hi}, they are often discouraged in risk averse traditional academia \cite{Sung2003-go}.

\noindent\textbf{Recruitment and Networking}: Hack weeks are often a melting pot of participants from academia, government, and industry and provide numerous opportunities for networking. Close collaboration in diverse groups exposes skills that might be suitable for careers outside of one's narrow domain.

\noindent\textbf{It's fun}: Hack weeks provide a respite from day-to-day research activities and provide a low-stress venue to learn new skills and attempt high-risk projects.

>>>>

\noindent\textbf{Education and Training}: While some hack weeks are more focused more on education than others (see Figure \ref{fig:hackspectrum}), skill-development cin the form of tutorials and informal and peer learning is often a component. Furthermore, lateral knowledge transfer \cite{b:wilson-swc-lessons-2016} through collaboration provides an opportunity to learn skills that are not described in papers and software implementations.

@@

\noindent\textbf{Community Building}: Hack weeks are an opportunity to catalyze community development through shared interest in solving computational challenges with open source software. They allow computationally-minded researchers to break from the isolation of their institutions and spark new collaborations.

\noindent\textbf{Interdisciplinary research}: Intensive, time-bounded collaborative events are an opportunity to experiment with concepts, questions, and methods that span boundaries within and across disciplines. Despite the fact that interdisciplinary experiments are impactful \cite{Hall2012-hi}, they are often discouraged in academic environments \cite{Sung2003-go}.

\noindent\textbf{Recruitment and Networking}: Hack weeks are a melting pot of participants from academia, government, and industry and provide numerous opportunities for networking. Close collaboration in diverse groups exposes skills that might be suitable for careers outside of a narrow domain.

\noindent\textbf{It's fun}: Hack weeks provide a respite from routine and provide a low-stress venue to learn new skills and attempt high-risk projects.
